FoRTE baseline

### 2019-09-12 analysis/paper/paper.Rmd
Add possible TODOs about Fifugre 3
Draft first discussion paragraph

@@

- Parameter uncertainty is the dominant driver of model predictive uncertainty.
- ...but the nature of this parameter uncertainty depends on model configuration.

>>>>

<!-- TODO Use peak instead of post-1975? -->
<!-- TODO Use a logarithmic, rather than a linear fit? -->

@@

The overarching objective of this study was to investigate how model structure and parameters interact in multidecadal simulations of forest ecosystem productivity and community assembly.

## ED2.2 vs. reality

Our first question was: To what extent can the model, under any configuration, reproduce the observed reality?
**Ensemble mean trajectory matches traditional understanding of succession**---rapid growth to peak productivity, followed by gradual decline [@odum_1969_strategy_ecosystem_development]---but **happens too quickly** (Figure 2);
real ecosystems sustain peak productivity for longer [@gough_2016_disturbance].
This idea that ED2.2's main issue is that it is moving too quickly is supported by the fact that ED2.2 generally **underestimates productivity after 100 years**, but model **predictions at peak productivity are close to reality**.
One reason ED2.2 is moving too quickly through succession is **missing mechanisms for sustaining productivity through early succession**.
In particular, recent evidence points to the **important role of low-severity, high-frequency disturbances** in sustaining ecosystem productivity [@gough_2016_disturbance].
ED2.2 has a mortality scheme, and indeed, parameters related to mortality were often among the top 10 most important parameters for predictive uncertainty (Figure 6).
<!-- Maybe move this elsewhere? -->
<!-- TODO Look at mortality across ED runs. Does it relate at all to results? -->
However, **our simulations did not include other sources of disturbance**, such as partial harvests, extreme weather, and damage from insects and pathogens, which are common to this region [@amiro_2010_ecosystem] and which may contribute to sustaining productivity and dominance of early-successional forests [@gough_2016_disturbance].
- Parameter uncertainty is the dominant driver of model predictive uncertainty.
- ...but the nature of this parameter uncertainty depends on model configuration.
